---
title: "stats"
output: html_document
---

In this notebook, we generate a CSV table that contains all the metrics we 
include in the final paper. First, we generate a couple of variables by 
category, then we generate other variables on a per-need basis section by 
section.

## ToDo

1. Read data and setup
2. Basic information
3. Count number of ties for key actors
4. Unweighted fractions of fossil fuel funders
5. Unweighted fractions of fossil fuel funders to key centers
5. Weighted funder fractions
6. Disclosure stats
7. More stats on fossil fuel sector
8. Write

## 1. Read data and setup

```{r libraries, message = F}
library(here)
library(tidyverse)
```

```{r read}
centers <- read_csv(here("data", "centers.csv"))
funders <- read_csv(here("data", "funders.csv")) %>% 
  left_join(select(centers, abbr, uni), by = "abbr")
glimpse(funders)
```

```{r setup}
vars <- tribble(
  ~var, ~value, 
  ~description
)
ff_producers <- "Fossil Fuel Producers"
ff_utilities <- "Fossil Fuel Utilities"
ff_vehicles <- "Fossil Fuel Vehicle Manufacturers"
```

## 2. Basic information

```{r basic}
ff_candidates <- "32411|211|213111|213112|4247|486|221|3361|3362|3363"
n_unique <- function(vector){
  length(unique(vector))
}

n_ff_companies <- n_unique(subset(funders, ff)$funder)
n_corp_funders <-  n_unique(subset(funders, corp)$funder)

basic <- tribble(
  ~var, ~value, 
  ~description,
  "n_centers", n_unique(centers$abbr),
  "Number of centers in our sample",
  "n_funders", n_unique(funders$funder), 
  "Number of identified unique funders", 
  "n_companies", n_unique(subset(funders, corp & is.na(notes))$funder),
  "Number of corporate funders excluding trade associations",
  "n_trade", n_unique(subset(funders, corp & notes == "Trade association")$funder),
  "Number of trade associations in the sample",
  "n_corp_foundations", n_unique(subset(funders, corp & str_starts(notes, "Via"))$funder),
  "Number of corporate foundations in the sample",
  "n_corp_funders", n_corp_funders,
  "Number of identified corporate funders",
  "n_corp_ties", nrow(subset(funders, corp)), 
  "Number of unique ties between corporate funders and centers",
  "n_trade_assoc", n_unique(subset(funders, notes == "Trade association")$funder),
  "Number of identified trade organizations", 
  "n_not_ff_candidates", n_unique(
    subset(funders, corp & !str_starts(naics, ff_candidates))$funder),
  "Number of corporate funders in industries that we did not probe for fossil fuel interests",
  "n_not_ff_candidate_industries", n_unique(
    subset(funders, corp & !str_starts(naics, ff_candidates))$industry),
  "Number of industries that we did not probe for fossil fuel interests",
  "n_ff_candidates", n_unique(
    subset(funders, corp & str_starts(naics, ff_candidates))$funder),
  "Number of corporate funders in the fossil fuel interest candidate industries", 
  "n_ff_companies", n_ff_companies,
  "Number of corporate funders in our sample that are part of the Fossil Fuel Sector",
  "n_ff_producers", n_unique(
    subset(funders, industry == ff_producers)$funder),
  "Number of Fossil Fuel Producers in our sample", 
  "n_ff_ties", nrow(subset(funders, ff)), 
  "Number of unique ties between Fossil Fuel Sector companies and centers", 
  "n_ff_centers", n_unique(subset(funders, ff)$abbr),
  "Number of research centers with ties to Fossil Fuel Sector companies",
  "n_ff_utilities", n_unique(
    subset(funders, industry == ff_utilities)$funder),
  "Number of Fossil Fuel Utilities in our sample", 
  "n_other_utilities", n_unique(
    subset(funders, industry == "Other Utilities")$funder),
  "Number of utilities that we did not code as Fossil Fuel Utilities", 
  "n_ff_vehicles", n_unique(
    subset(funders, industry == ff_vehicles)$funder),
  "Number of Fossil Fuel Vehicle Manufacturers in our sample", 
  "n_non_ff_vehicles", n_unique(
    subset(funders, str_starts(naics, ff_candidates) 
           & industry == "Miscellaneous Manufacturing")$funder),
  "Number of car manufacturers that we did not code as Fossil Fuel Vehicle Manufacturers", 
  "n_ff_vehicle_candidates", n_unique(
    subset(funders, str_starts(naics, "3361|3362|3363"))$funder),
  "Number of car manufacturers and suppliers in our sample that we probed for fossil fuel interests",
  "n_ff_utility_candidates", n_unique(subset(funders, str_starts(naics, "221"))$funder),
  "Number of utility companies in our sample that we probed for fossil fuel interests",
  "n_centers_harvard", nrow(subset(centers, uni == "Harvard University")),
  "Total number of centers in sample at Harvard",
  "n_centers_mit",  nrow(subset(centers, uni == "MIT")),
  "Total number of centers in sample at MIT",
  "n_centers_stanford", nrow(subset(centers, uni == "Stanford University")),
  "Total number of centers in sample at Stanford", 
  "n_centers_berkeley", nrow(subset(centers, uni == "UC Berkeley")),
  "Total number of centers in sample at UC Berkeley"
) %>%
  mutate(value = as.character(value))

basic_shares <- tribble(
  ~var, ~value,
  ~description,
  "ff_company_share", scales::percent(n_ff_companies/n_corp_funders, accuracy = 1),
  "Fossil Fuel Sector companies' share of total unique corporate funders in our sample"
)
vars <- bind_rows(vars, basic, basic_shares)
bind_rows(basic, basic_shares)
```

Key metrics for Fossil Fuel Sector industries and comparison points

```{r ff_key}
ff_utility_share <- n_unique(subset(funders, industry == ff_utilities)$funder) /
  n_corp_funders
consulting_share <- n_unique(subset(funders, industry == "Consulting")$funder) /
  n_corp_funders
electronics_share <- n_unique(subset(funders, industry == "Electronics")$funder) /
  n_corp_funders
ff_producers_share <- n_unique(subset(funders, industry == ff_producers)$funder) /
  n_corp_funders
more_shares <- tribble(
  ~var, ~value, 
  ~description, 
  "ff_utility_share", ff_utility_share, 
  "Share of Fossil Fuel Utilities' among total unique identified funders",
  "consulting_share", consulting_share, 
  "Share of consulting companies' among total unique identified funders",
  "electronics_share", electronics_share, 
  "Share of electronics firms among total unique identified funders", 
  "ff_producers_share", ff_producers_share, 
  "Share of Fossil Fuel Producers among total unique identified funders"
  ) %>%
  mutate(value = scales::percent(value, accuracy = 1))

reference_counts <- tribble(
  ~var, ~value, 
  ~description, 
  "consulting_total", n_unique(subset(funders, industry == "Consulting")$funder),
  "Number of unique consulting companies in our sample", 
  "electronics_total", n_unique(subset(funders, industry == "Electronics")$funder),
  "Number of unique electronics companies in our sample"
  ) %>%
  mutate(value = as.character(value))

vars <- bind_rows(vars, more_shares, reference_counts)
bind_rows(more_shares, reference_counts)
```

A few additional count of non-corporate ties

```{r tie_counts}
indiv_ties <- funders %>%
  filter(industry == "Individuals") %>%
  distinct(funder, abbr) %>%
  {nrow(.)}
ngo_ties <- funders %>%
  filter(industry == "NGOs/Foundations") %>%
  distinct(funder, abbr) %>%
  {nrow(.)}
gov_ties <- funders %>%
  filter(industry == "Government/National Lab") %>%
  distinct(funder, abbr) %>%
  {nrow(.)}

additional_tie_counts <- tribble(
  ~var, ~value, 
  ~description,
  "indiv_ties", indiv_ties,
  "Number of unique individuals or families in our sample",
  "ngo_ties", ngo_ties,
  "Number of unique NGOs, foundations etc. in our sample",  
  "gov_ties", gov_ties,
  "Number of unique government entities and national labs in our sample"
) %>%
  mutate(value = as.character(value))

vars <- bind_rows(vars, additional_tie_counts)
additional_tie_counts
```

## 3. Count number of ties and funder fractions for key actors

```{r top_funders}
ties <- distinct(funders, funder, abbr, ff, corp)
count_ties <- function(specific_funder){
  as.character(nrow(filter(funders, funder == specific_funder)))
}

top_funders <- tribble(
  ~var, ~value, 
  ~description,
  "exxonmobil_ties", count_ties("ExxonMobil"), 
  "Number of ties between ExxonMobil and centers", 
  "shell_ties", count_ties("Shell"),
  "Number of ties between Shell and centers",
  "chevron_ties", count_ties("Chevron"),
  "Number of ties between Chevron and centers",
  "bp_ties", count_ties("BP"),
  "Number of ties between BP and centers",
  "conocophillips_ties", count_ties("ConocoPhillips"),
  "Number of ties between ConocoPhillips and centers",
  "schlumberger_ties", count_ties("Schlumberger"),
  "Number of ties between Schlumberger and centers",
  "total_ties", count_ties("Total"),
  "Number of ties between TotalEnergies and centers",
  "pgande_ties", count_ties("Pacific Gas and Electric Company"),
  "Number of ties between PG&E and centers",
  "duke_ties", count_ties("Duke Energy"),
  "Number of ties between Duke Energy and centers",
  "engie_ties", count_ties("ENGIE"),
  "Number of ties between ENGIE and centers",
  "enel_ties", count_ties("Enel"),
  "Number of ties between Enel and centers",
  "toyota_ties", count_ties("Toyota"),
  "Number of ties between Toyota and centers",
  "boa_ties", count_ties("Bank of America"),
  "Number of ties between Bank of America and centers"
  )
vars <- bind_rows(vars, top_funders)
top_funders
```

## 4. Unweighted fractions of fossil fuel funders

```{r sector_ties}
ind_ties <- funders %>%
  filter(corp) %>%
  distinct(corp, funder, industry, abbr, ff, corp)
ind_counts <- ind_ties %>%
  count(industry)
count_ind_ties <- function(specific_industry){
  ind_counts %>%
    filter(industry == specific_industry) %>%
    pull(n)
}
calc_ind_share <- function(specific_industry){
  scales::percent(subset(ind_counts, industry == specific_industry)$n /
                    sum(ind_counts$n), accuracy = 1)
}
tie_counts <- tribble(
  ~var, ~value, 
  ~description, 
  "total_corp_ties", nrow(ind_ties),
  "Total number of ties between corporations and centers", 
  "ff_sector_tie_total", sum(ind_ties$ff),
  "Fossil fuel sector total number of ties to centers",
  "ff_producers_tie_total", count_ind_ties(ff_producers),
  "Fossil fuel producers' total number of ties to centers",
  "ff_utility_tie_total", count_ind_ties(ff_utilities),
  "Fossil fuel utilities' total number of ties to centers",
  "ff_vehicle_tie_total", count_ind_ties(ff_vehicles),
  "Fossil fuel vehicle manufacturers' total number of ties to centers"
  ) %>%
  mutate(value = as.character(value))

tie_shares <- tribble(
  ~var, ~value,
  ~description,
  "ff_sector_tie_share", scales::percent(sum(ind_ties$ff) / nrow(ind_ties), accuracy = 1),
  "Fossil fuel sector's share of total ties between corporations and centers",
  "ff_producers_tie_share", calc_ind_share(ff_producers),
  "Fossil fuel producers' share of total ties between corporations and centers",
  "ff_utility_tie_share", calc_ind_share(ff_utilities),
  "Fossil fuel utilities' share of total ties between corporations and centers",
  "ff_vehicle_tie_share", calc_ind_share(ff_vehicles),
  "Fossil fuel vehicle manufacturers' share of total ties between corporations and centers"
)

ind_ranks_raw <- funders %>%
  filter(corp) %>%
  distinct(funder, ff, industry) %>%
  count(industry) %>%
  arrange(desc(n)) %>%
  mutate(rank = min_rank(desc(n)))

ind_ranks <- tribble(
  ~var, ~value, 
  ~description,
  "consulting_rank", subset(ind_ranks_raw, industry == "Consulting")$rank,
  "Rank of consulting industry when ranking all industries by number of funders",
  "electronics_rank", subset(ind_ranks_raw, industry == "Electronics")$rank,
  "Rank of electronics industry when ranking all industries by number of funders",
  "ff_utilities_rank", subset(ind_ranks_raw, industry == ff_utilities)$rank,
  "Rank of Fossil Fuel Utilities when ranking all industries by number of funders",
  "ff_producers_rank", subset(ind_ranks_raw, industry == ff_producers)$rank,
  "Rank of Fossil Fuel Producers when ranking all industries by number of funders"
  ) %>%
  mutate(value = as.character(value))


vars <- bind_rows(vars, tie_counts, tie_shares, ind_ranks)
bind_rows(tie_counts, tie_shares, ind_ranks)
```

## 5. Unweighted fractions of fossil fuel funders to key centers

```{r center_ties}
count_center_ties <- function(specific_abbr){
  as.character(nrow(filter(ties, corp & abbr == specific_abbr)))
}
count_center_ff <- function(specific_abbr){
  as.character(nrow(filter(ties, ff & abbr == specific_abbr)))
}
share_center_ff <- function(specific_abbr){
  filter(ties, corp & abbr == specific_abbr) %>%
    {scales::percent(sum(.$ff) / nrow(.))}
}
center_ties <- tribble(
  ~var, ~value, 
  ~description,
  "hepg_ties", count_center_ties("HEPG"), 
  "HEPG total number of ties",
  "hepg_ff", count_center_ff("HEPG"), 
  "HEPG number of fossil fuel ties", 
  "hepg_share", share_center_ff("HEPG"), 
  "HEPG share of fossil fuel ties", 
  "heep_ties", count_center_ties("HEEP"), 
  "HEEP total number of ties", 
  "heep_ff", count_center_ff("HEEP"), 
  "HEEP number of fossil fuel ties", 
  "heep_share", share_center_ff("HEEP"), 
  "HEEP share of fossil fuel ties",
  "mitei_ties", count_center_ties("MITEI"), 
  "MITEI total number of ties", 
  "mitei_ff", count_center_ff("MITEI"), 
  "MITEI number of fossil fuel ties", 
  "mitei_share", share_center_ff("MITEI"), 
  "MITEI share of fossil fuel ties",
  "ceepr_ties", count_center_ties("CEEPR"), 
  "CEEPR total number of ties", 
  "ceepr_ff", count_center_ff("CEEPR"), 
  "CEEPR number of fossil fuel ties", 
  "ceepr_share", share_center_ff("CEEPR"), 
  "CEEPR share of fossil fuel ties",
  "jpspgc_ties", count_center_ties("JPSPGC"), 
  "JPSPGC total number of ties", 
  "jpspgc_ff", count_center_ff("JPSPGC"), 
  "JPSPGC number of fossil fuel ties", 
  "jpspgc_share", share_center_ff("JPSPGC"), 
  "JPSPGC share of fossil fuel ties",
  "ngi_ties", count_center_ties("NGI"), 
  "NGI total number of ties", 
  "ngi_ff", count_center_ff("NGI"), 
  "NGI number of fossil fuel ties", 
  "ngi_share", share_center_ff("NGI"), 
  "NGI share of fossil fuel ties",
  "emf_ties", count_center_ties("EMF"), 
  "EMF total number of ties", 
  "emf_ff", count_center_ff("EMF"), 
  "EMF number of fossil fuel ties", 
  "emf_share", share_center_ff("EMF"), 
  "EMF share of fossil fuel ties",
  "path_ties", count_center_ties("PATH"), 
  "PATH total number of ties", 
  "path_ff", count_center_ff("PATH"), 
  "PATH number of fossil fuel ties", 
  "path_share", share_center_ff("PATH"), 
  "PATH share of fossil fuel ties",
  "eihaas_ties", count_center_ties("EI@Haas"), 
  "EI@Haas total number of ties", 
  "eihaas_ff", count_center_ff("EI@Haas"), 
  "EI@Haas number of fossil fuel ties", 
  "eihaas_share", share_center_ff("EI@Haas"), 
  "EI@Haas share of fossil fuel ties",
  "ebi_ties", count_center_ties("EBI"), 
  "EBI total number of ties", 
  "ebi_ff", count_center_ff("EBI"), 
  "EBI number of fossil fuel ties", 
  "ebi_share", share_center_ff("EBI"), 
  "EBI share of fossil fuel ties",
)
vars <- bind_rows(vars, center_ties)
center_ties
```

## 6. Weighted funder fractions

```{r weight}
source(here("util", "weight_fractions.R"))
calculate_ff_weight <- function(df, filter_condition) {
  filter_condition <- enquo(filter_condition)
  df %>%
    filter(corp) %>%
    weight_fractions(centers, rm_no_disclosure = T) %>%
    group_by(industry, ff) %>%
    summarize(weighted_fraction = sum(weighted_fraction), .groups = "drop") %>%
    filter(!!filter_condition) %>%
    {scales::percent(sum(.$weighted_fraction), accuracy = 1)}
}
weight_stats <- tribble(
  ~var, ~value, 
  ~description,
  "across_ff_weight", calculate_ff_weight(funders, ff),
  "Weighted funder fraction of the Fossil Fuel Sector among industry funders across universities",
  "harvard_ff_weight", calculate_ff_weight(subset(funders, uni == "Harvard University"), ff),
  "Weighted funder fraction of the Fossil Fuel Sector among industry funders at Harvard university",
  "mit_ff_weight", calculate_ff_weight(subset(funders, uni == "MIT"), ff),
  "Weighted funder fraction of the Fossil Fuel Sector among industry funders at MIT",
  "stanford_ff_weight", calculate_ff_weight(subset(funders, uni == "Stanford University"), ff),
  "Weighted funder fraction of the Fossil Fuel Sector among industry funders at Stanford University",
  "berkeley_ff_weight", calculate_ff_weight(subset(funders, uni == "UC Berkeley"), ff),
  "Weighted funder fraction of the Fossil Fuel Sector among industry funders at UC Berkeley",
  "harvard_ff_producers_weight", calculate_ff_weight(
    subset(funders, uni == "Harvard University"),
    industry == ff_producers),
  "Weighted funder fraction of Fossil Fuel Producers among industry funders at Harvard University", 
  "harvard_ff_utilities_weight", calculate_ff_weight(
    subset(funders, uni == "Harvard University"),
    industry == ff_utilities),
  "Weighted funder fraction of Fossil Fuel Utilities among industry funders at Harvard University", 
  "mit_ff_producers_weight", calculate_ff_weight(
    subset(funders, uni == "MIT"),
    industry == ff_producers),
  "Weighted funder fraction of Fossil Fuel Producers among industry funders at MIT", 
  "mit_ff_utilities_weight", calculate_ff_weight(
    subset(funders, uni == "MIT"),
    industry == ff_utilities),
  "Weighted funder fraction of Fossil Fuel Utilities among industry funders at MIT", 
  "mit_ff_vehicles_weight", calculate_ff_weight(
    subset(funders, uni == "MIT"),
    industry == ff_vehicles),
  "Weighted funder fraction of Fossil Fuel Vehicle Manufacturers among industry funders at MIT", 
  
  
) 
vars <- bind_rows(vars, weight_stats)
weight_stats
```

## 7. Disclosure stats

```{r disclosure}
count_no_disclosure <- function(specific_uni){
  uni_df <- filter(funders, str_detect(uni, specific_uni))
  subset(centers, str_detect(uni, specific_uni) & !abbr %in% uni_df$abbr) |>
    nrow()
}
calc_share_no_disclosure <- function(specific_uni){
  uni_df <- filter(funders, str_detect(uni, specific_uni))
  n_no_disclosure <- subset(
    centers, 
    str_detect(uni, specific_uni) & !abbr %in% uni_df$abbr
    ) |>
    nrow()
  n_no_disclosure / nrow(subset(centers, str_detect(uni, specific_uni)))
}

no_disclosure_counts <- tribble(
  ~var, ~value, 
  ~description, 
  "n_no_disclosure", count_no_disclosure(".*"),
  "Number of centers across all universities that do not disclose any funders",
  "n_no_disclosure_harvard", count_no_disclosure("Harvard University"), 
  "Number of centers at Harvard that do not disclose any funders",
  "n_no_disclosure_mit", count_no_disclosure("MIT"), 
  "Number of centers at MIT that do not disclose any funders",
  "n_no_disclosure_stanford", count_no_disclosure("Stanford University"), 
  "Number of centers at Stanford University that do not disclose any funders",
  "n_no_disclosure_berkely", count_no_disclosure("UC Berkeley"), 
  "Number of centers at UC Berkeley that do not disclose any funders",
  "berkeley_n_disclosure", nrow(subset(centers, uni == "UC Berkeley")) -
    count_no_disclosure("UC Berkeley"),
  "Number of centers at UC Berkeley that disclose funders",
  "mit_n_disclosure", nrow(subset(centers, uni == "MIT")) -
    count_no_disclosure("MIT"),
  "Number of centers at MIT that disclose funders"
) %>%
  mutate(value = as.character(value))

no_disclosure_shares <- tribble(
  ~var, ~value, 
  ~description, 
  "share_no_disclosure", calc_share_no_disclosure(".*"),
  "Share of centers across all universities that do not disclose any funders",
  "share_centers_harvard_no_disclosure", calc_share_no_disclosure(
    "Harvard University"),
  "Share of centers at Harvard University that do not disclose any funders",
  "share_centers_mit_no_disclosure", calc_share_no_disclosure("MIT"),
  "Share of centers at MIT that do not disclose any funders",
  "share_centers_stanford_no_disclosure", calc_share_no_disclosure(
    "Stanford University"),
  "Share of centers at Stanford University that do not disclose any funders",
  "share_centers_berkeley_no_disclosure", calc_share_no_disclosure(
    "UC Berkeley"),
  "Share of centers at UC Berkeley that do not disclose any funders",
  "berkeley_share_disclosure", 1 - calc_share_no_disclosure("UC Berkeley"),
  "Share of centers at UC Berkeley that disclose funders",
  "mit_share_disclosure", 1 - calc_share_no_disclosure("MIT"),
  "Share of centers at MIT that disclose funders",
) %>%
  mutate(value = scales::percent(value, accuracy = 1))
vars <- bind_rows(vars, no_disclosure_counts, no_disclosure_shares)
bind_rows(no_disclosure_counts, no_disclosure_shares)
```

## 8. Specific Fossil Fuel Sector stats

```{r ff_stats}
mitei_funder_count <- funders %>%
  filter(abbr == "MITEI") %>%
  distinct(funder) %>%
  {nrow(.)}
mitei_ff_count <- funders %>%
  filter(abbr == "MITEI" & ff) %>%
  distinct(funder) %>%
  {nrow(.)}
mitei_ff_producers <- funders %>%
  filter(abbr == "MITEI" & industry == ff_producers) %>%
  distinct(funder) %>%
  {nrow(.)}
berkeley_funder_count <- funders %>%
  filter(uni == "UC Berkeley") %>%
  distinct(funder) %>%
  {nrow(.)}
berkeley_tie_count <- funders %>%
  filter(uni == "UC Berkeley") %>%
  distinct(funder, abbr) %>%
  {nrow(.)}
berkeley_ff_count <- funders %>%
  filter(uni == "UC Berkeley" & ff) %>%
  distinct(funder) %>%
  {nrow(.)}
berkeley_ff_producers <- funders %>%
  filter(uni == "UC Berkeley" & industry == ff_producers) %>%
  distinct(funder) %>%
  {nrow(.)}
berkeley_ff_producers_ties <- funders %>%
  filter(uni == "UC Berkeley" & industry == ff_producers) %>%
  distinct(funder, abbr) %>%
  {nrow(.)}

ff_extra_stats <- tribble(
  ~var, ~value,
  ~description,
  "mitei_funder_count", as.character(mitei_funder_count), 
  "Number of unique funders of MITEI", 
  "mitei_ff_count", as.character(mitei_ff_count),
  "Number of Fossil Fuel Sector funders at MITEI", 
  "mitei_ff_producers", as.character(mitei_ff_producers),
  "Number of Fossil Fuel Producers funders at MITEI", 
  "mitei_ff_share", scales::percent(mitei_ff_count / mitei_funder_count, accuracy = 1),
  "Share of Fossil Fuel Sector funders at MITEI",
  "mitei_ff_producers_share", scales::percent(mitei_ff_producers / mitei_funder_count, accuracy = 1),
  "Share of Fossil Fuel Producers funders at MITEI",
  "berkeley_funder_count", as.character(berkeley_funder_count), 
  "Number of unique funders of UC Berkeley", 
  "berkeley_tie_count", as.character(berkeley_tie_count),
  "Number of ties between centers and funders for UC Berkeley",
  "berekeley_ff_count", as.character(berkeley_ff_count),
  "Number of Fossil Fuel Sector funders at UC Berkeley", 
  "berkeley_ff_producers", as.character(berkeley_ff_producers),
  "Number of Fossil Fuel Producers funders at UC Berkeley", 
  "berkeley_ff_producers_ties", as.character(berkeley_ff_producers_ties),
  "Number of ties between Fossil Fuel Producers and centers at UC Berkeley", 
  "berekeley_ff_share", scales::percent(berkeley_ff_count / berkeley_funder_count),
  "Share of Fossil Fuel Sector funders at UC Berkeley",
  "berekeley_ff_producers_share", scales::percent(berkeley_ff_producers / berkeley_funder_count),
  "Share of Fossil Fuel Producers funders at UC Berkeley",
  "berekeley_ff_producers_tie_share", scales::percent(berkeley_ff_producers_ties / berkeley_tie_count),
  "Share of Fossil Fuel Producers funders of total ties at UC Berkeley"
)
vars <- bind_rows(vars, ff_extra_stats)
ff_extra_stats
```

## 9. Various

```{r gov_overlap}
n_gov_centers <- n_unique(subset(funders, industry == "Government/National Lab")$abbr)
n_gov_ff_centers <- funders %>%
  filter(industry == "Government/National Lab") %>%
  distinct(abbr) %>%
  inner_join(filter(funders, ff), by = "abbr", relationship = "one-to-many") %>%
  distinct(abbr) %>%
  {nrow(.)}
ff_sector_tie_share_all <- nrow(subset(funders, ff)) / nrow(funders)

gov_stat <- tribble(
  ~var, ~value,
  ~description,
  "n_gov_centers", as.character(n_gov_centers), 
  "Number of centers that receive funding from government agencies or national labs", 
  "n_gov_ff_centers", as.character(n_gov_ff_centers), 
  "Number of centers that receive funding from both government agencies/national labs and fossil fuel companies",
  "gov_ff_share", scales::percent(n_gov_ff_centers / n_gov_centers, accuracy = 1),
  "Share of centers of government/national lab-funded centers that also receive funding from Fossil Fuel Sector companies",
  "ff_sector_tie_share_all", scales::percent(ff_sector_tie_share_all, accuracy = 1),
  "Fossil fuel sector's share of total ties between corporate and non-corporate and centers"
) 
vars <- bind_rows(vars, gov_stat)
gov_stat
```

## 10. Write

```{r write}
write_csv(vars, here("out", "vars.csv"))
```
