---
title: "table_1"
output: html_document
---

```{r library}
library(tidyverse)
library(knitr)
library(kableExtra)
library(here)

if (!"jules.tools" %in% installed.packages()){
  devtools::install_github("julianbarg/jules.tools")
}
library(jules.tools)
```

## ToDo

1. Read input
2. Table 1 -- ranking by university and category
3. Table 2 -- cross-university counts

## 1. Read input

```{r read}
centers <- read_csv(here("data", "centers.csv"))
glimpse(centers)
cat("\n")
funders <- read_csv(here("data", "funders.csv")) %>%
  left_join(select(centers, abbr, uni), by = "abbr")
glimpse(funders)
```

## 2. Table 1 -- ranking by university and category

Here, we just want to compare across industries:

```{r corp}
corp_funders <- filter(funders, corp)
```

First, get the counts of funders. To get the counts across universities, 
we aggregate and then add the counts per university again at the bottom
with `bind_rows`.

```{r funder_counts}
funder_counts <- corp_funders %>%
  distinct(uni, industry, funder, ff) %>%
  group_by(uni, industry, ff) %>% 
  summarize(value = n(), .groups = "drop") %>%
  group_by(uni) %>%
  mutate(share = value / sum(value), 
         sector = sum(ff * value),
         sector_share = sum(ff * value) / sum(value)) %>%
  ungroup()
funder_counts <- funder_counts %>%
  group_by(industry, ff) %>%
  summarize(value = sum(value), .groups = "drop") %>%
  mutate(share = value / sum(value), 
         sector = sum(ff * value),
         sector_share = sum(ff * value) / sum(value)) %>%
  mutate(uni = "Across universities") %>%
  bind_rows(funder_counts) %>%
  mutate(metric = "funders")
glimpse(funder_counts)
```

Now, we do the same for the counts of unique ties between funders and centers.
Very much the same approach that we took for funder counts. We again
count by university, then aggregate across universities and use `bind_rows` to
add the per-university counts again.

```{r ties}
tie_counts <- corp_funders %>%
  distinct(uni, industry, funder, abbr, ff) %>%
  group_by(uni, industry, ff) %>%
  summarize(value = n(), .groups = "drop") %>%
  group_by(uni) %>%
  mutate(share = value / sum(value), 
         sector = sum(ff * value),
         sector_share = sum(ff * value) / sum(value)) %>%
  ungroup()
tie_counts <- tie_counts %>%
  group_by(industry, ff) %>%
  summarize(value = sum(value), .groups = "drop") %>%
  mutate(uni = "Across universities") %>%
  mutate(share = value / sum(value), 
         sector = sum(ff * value), 
         sector_share = sum(ff * value) / sum(value)) %>%
  bind_rows(tie_counts) %>%
  mutate(metric = "ties")
glimpse(tie_counts)
```

Calculate weights across universities and per university.

```{r weighted_fractions}
source(here("util", "weight_fractions.R"))
weights <- list()
weights$across <- weight_fractions(corp_funders, centers, rm_no_disclosure = T) %>%
  group_by(industry, ff) %>%
  summarize(value = sum(weighted_fraction), .groups = "drop") %>%
  mutate(uni = "All universities", 
         sector_share = sum(ff*value),
         share = value)
testthat::expect_equal(sum(weights$across$value), 1)
get_weights <- function(uni_){
  df <- filter(corp_funders, str_detect(uni, uni_))
  uni <- unique(df$uni)
  weights <- df %>%
    weight_fractions(filter(centers, str_detect(uni, uni_)), rm_no_disclosure = T) %>%
    group_by(industry, ff) %>%
    summarize(value = sum(weighted_fraction), .groups = "drop") %>%
    mutate(uni = uni) %>%
    group_by(uni) %>%
    mutate(sector_share = sum(ff * value), 
           share = value) %>%
    ungroup() 
  # Test that the normalization was correct:
  testthat::expect_equal(sum(weights$value), 1)
  weights
}
weights$harvard <- get_weights("Harvard")
weights$mit <- get_weights("MIT")
weights$stanford <- get_weights("Stanford")
weights$berkeley <- get_weights("Berkeley")
```

Calculate all the ranks.

```{r ranks}
ranks_table <- bind_rows(weights) %>%
  mutate(metric = "weighted fraction") %>%
  bind_rows(funder_counts, tie_counts) %>%
  group_by(uni, metric) %>%
  mutate(rank = as.integer(rank(-value))) %>%
  arrange(rank) %>%
  filter(ff) %>%
  slice_min(rank) %>%
  ungroup() %>%
  mutate(sector = scales::percent(sector_share, 1)) %>%
  mutate(rank = str_glue("{rank} ({scales::percent(share, 1)})")) %>%
  select(uni, metric, industry, rank, sector)
glimpse(ranks_table)
```

Generate the title. Note that we are not adding the full column names.
R would insert periods instead of spaces, so we add the full column names
manually later.

```{r write_ranks}
neat_names <- c("University" = "uni", 
                "Metric" = "metric",
                "Rank" = "rank", 
                "Sector" = "sector")

ranks_table %>%
  filter(uni != "Across universities") %>%
  mutate(metric = case_when(
    metric == "funders" ~ "Number of funders", 
    metric == "ties" ~ "Number of funding ties", 
    metric == "weighted fraction" ~ "Weighted funder fraction"
  )) %>%
  group_by(uni) %>%
  mutate(uni = if_else(row_number() == 1, uni, "")) %>%
  ungroup() %>%
  mutate(metric = 
           case_when(metric == "funders" ~ "Number of funders", 
                     metric == "ties" ~ "Number of funding ties",
                     metric == "weighted fraction" ~ "Weighted funder fraction")) %>%
  rename(!!! neat_names) %>% 
  jules.tools::make_pandoc_table(here("out", "table_1_ranks.md"))
```

## 3. Table 2 -- cross-university counts

Creating a dataframe with the appropriate data and then exporting to markdown,
to be converted to word or other formats as needed with `pandoc`.
Note that in the column titles, this produces "Harvard" instead of "Harvard 
University", same for "Stanford University", "UC Berkeley" and "All 
Universities." That is because otherwise R would insert a period where the 
space is when we `pivot_wider`. We manually fix this in the markdown output.

```{r table_1}
group_better <- c("ff" = "Fossil Fuel\nSector",
                  "corp" = "All other\ncorporate",
                  "gov" = "Government &\nnational labs", 
                  "indv" = "Individuals", 
                  "NGO" = "Third sector", 
                  "uni" = "Universities", 
                  "total" = "Total funding\nties")
total_ties <- nrow(funders)
total_by_uni <- funders %>%
  group_by(uni) %>%
  summarize(total = n())

funders_grouped <- funders %>%
  mutate(group = case_when(
    ff ~ "ff",
    corp ~ "corp", 
    industry == "Government/National Lab" ~"gov",
    industry == "Individuals" ~ "indv",
    industry == "NGOs/Foundations" ~ "NGO",
    industry == "Universities" ~ "uni"
  ))
funders_by_uni <- funders_grouped %>%
  group_by(uni, group) %>%
  summarize(n = n(), .groups = "drop") %>%
  group_by(uni) %>%
  mutate(n = str_glue("{n} ({scales::percent(n/sum(n), 1)})")) %>%
  ungroup()
funders_across <- funders_grouped %>%
  group_by(group) %>%
  summarize(n = n(), .groups = "drop") %>%
  mutate(uni = "Universities") %>%
  mutate(n = str_glue("{n} ({scales::percent(n/sum(n), 1)})"))
funders_total <- funders %>%
  group_by(uni) %>%
  summarize(n = n()) %>%
  mutate(group = "total") %>%
  {add_row(., uni = "Universities", n = sum(.$n), group = "total")} %>%
  # {add_row(., uni = "Across Universities", n = sum(.$n), group = "total")} %>%
  mutate(n = as.character(n))
subindustry <- funders %>%
  filter(ff) %>%
  group_by(uni, industry) %>%
  summarize(n = n(), .groups = "drop") %>%
  left_join(total_by_uni, by = "uni") %>%
  mutate(n = str_glue("{n} ({scales::percent(n/total, 1)})")) %>%
  select(-total)
subind_w_total <- funders %>%
  filter(ff) %>%
  group_by(industry) %>%
  summarize(
    n = str_glue("{n()} ({scales::percent(n()/total_ties, 1)})")) %>%
  # Should be "All Universities," see explanation above.
  mutate(uni = "Universities") %>%
  bind_rows(subindustry) %>%
  mutate(subindustry = industry, 
         group = "ff_sub") %>%
  select(-industry)
sector_table <- bind_rows(funders_across, subind_w_total, funders_by_uni, 
          funders_total) %>%
  mutate(uni = case_when(
    uni == "Harvard University" ~ "Harvard", 
    uni == "UC Berkeley" ~ "Berkeley", 
    uni == "Stanford University" ~ "Stanford", 
    T ~ uni
  )) %>%
  mutate(uni = factor(uni, levels = c("Harvard", "MIT", "Stanford", "Berkeley", "Universities"))) %>%
  arrange(uni) %>%
  pivot_wider(names_from = uni, values_from = n) %>%
  mutate(group = factor(group, levels = c(
    "ff", "ff_sub", "corp", "gov", "indv", "NGO", "uni", "total"))) %>%
  mutate(across(.cols = c(Harvard, MIT, Stanford, `Berkeley`),
  # mutate(across(.cols = c(Harvard, MIT, Stanford, `UC Berkeley`),
                ~replace_na(.x, "0 (0%)"))) %>%
  arrange(group) %>%
  mutate(group = recode(group, !!!group_better)) %>%
  rename(Sector = group, Industry = "subindustry") %>%
  mutate(
    Industry = if_else(is.na(Industry), " ", Industry))
sector_table
jules.tools::make_pandoc_table(sector_table, here("out", "table_2_sectors.md"))
```































